Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-22 tex/v3/appendix.tex
seperate suppl

\subsection{Proof of Lemma~\ref{lemma_actives_sets}}

@@

\subsection{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}

@@

\subsection{Proof of Proposition~\ref{proposition_error_in_marginals}}

@@

\subsection{Proof of Proposition~\ref{prop:objective-error}}

@@

\subsection{Additional experimental results}

>>>>

\section{Proof of Lemma~\ref{lemma_actives_sets}}

@@

\section{Proof of Proposition~\ref{prop:bounds_of_usc_and_vsc}}

@@

\section{Proof of Proposition~\ref{proposition_error_in_marginals}}

@@

\section{Proof of Proposition~\ref{prop:objective-error}}

@@

\section{Additional experimental results}
